mixModelE1data

### 2018-08-19 E2/analysis/importE2data.Rmd
progress

>>>>

Rename some columns
```{r }
E<- data
names(E)[names(E) == 'target'] <-'stream'
names(E)[names(E) == 'condition'] <-'orientation'
E$stream[ E$stream==1 ] <- "Left"
E$stream[ E$stream==2 ] <- "Right"
E$targetSide[ E$targetSide==0 ] <- "Both"
E$targetSide[ E$targetSide==1 ] <- "Left"
E$targetSide[ E$targetSide==2 ] <- "Right"

#mutate condition to Orientation
E$orientation[ E$orientation==1 ] <- "Canonical"
E$orientation[ E$orientation==2 ] <- "Inverted"
```

### 2018-08-19 E2/analysis/mixModelE2data.Rmd
progress

numItemsInStream<- length( data[1,"letterSeq"]$letterSeq$`1` )  
minSPE<- -17; maxSPE<- 17

@@

Try to analyze one bit of data.
```{r}
library(mixRSVP)
dg<-E2 %>% filter(subject=="AA")
dg<-dg %>% filter( !is.nan(targetSP) ) #excluding 1-target trials rows reporting stream on opposite side. Eventually, use those to evaluate swaps.

@@

estimates<- E2  %>%  filter( !is.nan(targetSP) ) %>% filter(subject>"AF") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

@@

>>>>

numItemsInStream<- length( data[1,"letterSeq"]$letterSeq$`1` )  
minSPE<- -17; maxSPE<- 17  #But it's 16 items in stream, so shouldn't it be -15, +15?

@@

Try to analyze one bit of data.
```{r}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)
library(mixRSVP)
dg<-E2 %>% filter(subject=="AA")
dg<-dg %>% filter( !is.nan(targetSP) ) #excluding 1-target trials rows reporting stream on opposite side. Eventually, use those to evaluate swaps.

@@

estimates<- E2  %>%  filter( !is.na(targetSP) ) %>%
    group_by_at(.vars = condtnVariableNames) %>%  
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

@@

Calc numObservations for each condition
```{r }
#Calc numObservations for each condition. This is needed  for scaling the fine-grained Gaussian
#gaussianScaledforData needs to know.
dfGroups<-  E2  %>%  filter( !is.na(targetSP) ) %>% group_by_at(.vars = condtnVariableNames) %>% summarise(nPerCond = n())
#add nPerCond back to parameter estimates
estimates<- merge(estimates,dfGroups)
```
